Forecasting climate change impacts on plant population dynamics at large spatial extents: a test case with sagebrush (\emph{Artemisia}) species

### 2015-11-03 docs/appendixB.Rmd
updates appendix B with mention of knot spacing

Spatial dependence existed in the residuals until pixels were separated by about 500 meters (Fig. B1). Thus, we set the kernal bandwidth ($\sigma$ in Eq. X of the main text) to 500/3 = `r round(500/3,2)`. We then placed equally-spaced knots across our spatial grid until the distance between nearest neighbors was approximately $\sigma$ = `r round(500/3,2)`. This resulted in 121 knots (Fig. B2).

>>>>

Spatial dependence existed in the residuals until pixels were separated by about 500 meters (Fig. B1). Thus, we set the kernal bandwidth ($\sigma$ in Eq. X of the main text) to 500/3 = `r round(500/3,2)`. We then placed equally-spaced knots across our spatial grid until the distance between nearest neighbors was approximately $\sigma$ = `r round(500/3,2)`. Knots were placed evenly across space in the sense that all pixels are equally-spaced along latitude and longitude, but the latitudinal distance and longitudinal distance are not exactly equal. This was done to achieve a symmetric grid of knots. This resulted in a 11 $\times$ 11 knot grid (121 knots; Fig. B2).
